---
title: "Zoom City Carbon Model"
author : "Berlin"
output: 
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/ByMaxAnjos"
    vertical_layout: scroll
    social: menu
    theme: yeti
---

```{r setup, include=FALSE}
# Importing libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(flexdashboard, shiny, tidyverse, data.table, highcharter, gt, htmltools,leaflet, sf, plotly, crosstalk, viridis, DT)

library(flexdashboard)
library(shiny)
library(tidyverse)
library(data.table)
library(highcharter)
library(sf)
library(gt)
library(htmltools)
library(viridis)
library(leaflet)
library(plotly)
library(crosstalk)
library(DT)

#Load files in dashboard folder 
imap <- st_read("dashboard/data/imap.shp")
trend <- fread("dashboard/data/trend.csv")
mapCount <- fread("dashboard/data/mapCount.csv")
amenity <- fread("dashboard/data/amenity.csv")
natural <- fread("dashboard/data/natural.csv")
leisure <- fread("dashboard/data/leisure.csv")
shop <- fread("dashboard/data/shop.csv")
place <- fread("dashboard/data/place.csv")
OSM_road <- fread("dashboard/data/OSM_raod.csv")
landuse <- fread("dashboard/data/landuse.csv")
street <- fread("dashboard/data/street.csv")
hour <- fread("dashboard/data/hour.csv")
find_street <- fread("dashboard/data/find_street.csv")
week <- fread("dashboard/data/week.csv")
iDistrict_map <- st_read("dashboard/data/iDistrict.shp")
iDistrict_tibble <- fread("dashboard/data/iDistrict_table.csv") %>% 
  dplyr::select(-osm_id)

```

# Sidebar {.sidebar}

The **Zoom City Carbon Model - ZCCM** is a high-resolution, bottom-up framework for quantifying urban CO₂ emissions at street-level granularity (100m grids). This interactive platform visualizes spatio-temporal emission patterns from key urban sources:Road traffic, Building energy, Human respiration, and Vegetation/soil interactions.

This **Emission Geographic Information platform** is designed to communicate the outcomes of the {ZCCM} to users, stakeholders, the research community, and the public in general. It enables the visualization of zoom CO2 maps and summary statistics of emissions in an interactive way.

This **Flexdashboard R** leverages road traffic estimates from the ZCCM::traffic model <https://github.com/ByMaxAnjos/CO2-traffic-emissions> to showcase the spatio-temporal variability of CO2 emissions at the city level. With this tool, users can explore detailed street-level emissions, emissions associated with Open Street Map features, and temporal patterns such as hourly time series, daily cycles, and monthly totals.

**Author: [Max Anjos](https://github.com/ByMaxAnjos).** Anjos M & Meier F (2025) Front. Environ. Sci.doi: [10.3389/fenvs.2024.1461656](https://doi.org/10.3389/fenvs.2024.1461656)

# Citywide Emissions {data-icon="fa-map-marked-alt"}

### Spatial Distribution {data-height="500"}

```{r fig.height=5}
# Prepare map data
imap <- imap %>% 
  mutate(
    label = glue::glue(
      "<strong>Street:</strong> {name}<br/>
      <strong>CO₂ Emissions:</strong> {round(tCO2, 1)} tCO₂/month"
    ) %>% lapply(htmltools::HTML),
    emission_quantile = cut(tCO2, quantile(tCO2, probs = seq(0, 1, 0.2)), 
                           include.lowest = TRUE)
  )

pal <- colorQuantile("RdYlBu", domain = imap$tCO2, n = 5, reverse = TRUE)

leaflet(imap, options = leafletOptions(zoomControl = FALSE)) %>%
  addProviderTiles("CartoDB.Positron", group = "Light") %>%
  addProviderTiles("Esri.WorldImagery", group = "Satellite") %>%
  addPolylines(
    color = ~pal(tCO2),
    weight = 2,
    opacity = 0.8,
    label = ~label,
    highlight = highlightOptions(
      weight = 3,
      color = "#333",
      bringToFront = TRUE
    )
  ) %>%
  addLegend(
    position = "bottomright",
    pal = pal,
    values = ~tCO2,
    title = "CO₂ Emissions<br>(t/month)",
    labFormat = labelFormat(suffix = " tCO₂"),
    opacity = 0.8
  ) %>%
  addLayersControl(
    baseGroups = c("Light", "Satellite"),
    position = "topleft",
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addMiniMap(toggleDisplay = TRUE)
```

### Temporal Trends

```{r fig.height=5}
highchart() %>% 
    hc_add_series(trend, hcaes(x = date_day, y = ktCO2, color = ktCO2), type = "spline") %>%
    hc_tooltip(crosshairs = TRUE, borderWidth = 1.5, headerFormat = "", pointFormat =
                 paste("Day: <b>{point.x}</b> <br> ktCO2: <b>{point.y}</b>")) %>%
    hc_title(text = "") %>% 
    hc_subtitle(text = "") %>%
    hc_xAxis(title = list(text = "Day")) %>%
    hc_yAxis(title = list(text = "Traffic emissions [ktCO2/day]"),
             allowDecimals = FALSE,
             plotLines = list(list(
                    color = "white", width = 1, dashStyle = "Dash", 
                    value = mean(trend$ktCO2),
                    label = list(text = "Mean = 10", 
                                 style = list(color = "white", fontSize = 11))))) %>%
    hc_legend(enabled = FALSE) %>% 
     hc_credits(
    enabled = TRUE, 
    text = "Zoom City Carbon Model | TU Berlin",
    href = "https://github.com/ByMaxAnjos"
  ) %>% hc_add_theme(hc_theme_google()) %>% 
    hc_exporting(enabled = TRUE)

```

# District Analysis {data-icon="fa-chart-pie"}

## District Selector {data-width="400"}

### Filter Districts

**Get here:**

```{r}
# Create shared data that will be used to link filters, data table, and line plot. 
  iDistrict_tibble$day <- as.numeric(iDistrict_tibble$day)
  shared_data <- SharedData$new(iDistrict_tibble, group = 'hello')
  
  # Create filter for year and district These filters will adjust the DT datatable and PLOTLY plot. 
  filter_slider("day", "Day", shared_data, ~day, step = 1)
  filter_select("district", "District", shared_data, ~district, allLevels = TRUE, multiple = TRUE)
  filter_checkbox(id = "district", label = "Select district", sharedData = shared_data, group = ~district, columns=2)
```

### Daily Emission Patterns

```{r}

# Set a random seed. We will do this so that we can reproduce the random sample of colors we will use for our next graph. 
set.seed(80085)

# Create line graph. 
plot_ly(shared_data, x = ~day, y = ~tCO2, 
       color = ~district, colors = sample(colours(), 120),
       type = 'scatter', mode = 'lines',
       hoverinfo = 'text', text = ~paste("District: ", 
                                         district, '<br>Day: ', day, "<br>tCO2: ", tCO2)) %>%
       layout(showlegend = FALSE,
              title = "trafiic emissions by Disrrict",
              xaxis = list(title = "Day"),
              yaxis = list(title = " tCO2")) %>%
       layout(plot_bgcolor = 'transparent') %>% 
       layout(paper_bgcolor = 'transparent') %>% 
       add_markers() %>% 
       highlight("plotly_click")
  
```

## District Map {data-width="600"}

### Interactive map

```{r map}

pal_line <- colorFactor(palette = "viridis", domain = NULL, reverse = TRUE)
iDistrict_map$labels <- paste0(
  "<strong> district: </strong> ",
  iDistrict_map$district, "<br/> ",
  "<strong> tCO2: </strong> ",
  iDistrict_map$tCO2, "<br/> "
) %>%
  lapply(htmltools::HTML)

leaflet(iDistrict_map) %>%
  addTiles(group = "OpenStreeMap.Default") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Esri.WorldImagery") %>%
  addProviderTiles("CartoDB.DarkMatter", group = "CartoDB.DarkMatter") %>%
  addPolygons(weight = 1, smoothFactor = 0.5,
    #fillColor = "tCO2",
    color = ~ pal_line(tCO2),
    opacity = 1.0, fillOpacity = 0.5,
    label = ~labels,
    highlight =  highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE)
  ) %>%
  leaflet::addLegend(pal = pal_line, values = "",title = "Traffic tCO2 emissions", group = "Total of tCO2") %>% 
  # layers control
  addLayersControl(
    baseGroups = c("OpenStreeMap.Default", "CartoDB.DarkMatter", "Esri.WorldImagery"),
    position = "topleft",
    options = layersControlOptions(collapsed = TRUE)
  )

```

### 

```{r}
set.seed(80085)
plot_ly(shared_data, y = ~tCO2, x = ~district, type = 'bar', color = ~district, colors = sample(colours(), 120)) %>%
       layout(yaxis = list(categoryorder = "trace"))

```

# Summary Stats {data-orientation="rows" data-icon="fa-bar-chart"}

## Row {data-height="100"}

## Row 1 {data-height="110"}

### Total of traffic emissions [ktCO2/month]

```{r}
#mapCount <- fread("mapCount.csv")

valueBox(round(sum(mapCount$ktCO2), digits = 2),icon = "fa-users", color = "purple")
```

### Total of carbon [ktC/month]

```{r}

valueBox(round(sum(mapCount$ktC), digits = 2), icon="fa-users", color = "purple")
```

## Row 2 {.tabset .tabset-fade}

### Top CO2 Amenity sites

```{r fig.height=5}
#amenity <- fread("amenity.csv")

# Colors
custom_colors <- viridis::plasma(n = length(amenity$amenity))

# Amenity Open Street Map feature
amenity %>% 
  hchart('bar', hcaes(x = amenity, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Amenity',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>%
 hc_xAxis(title = "") %>%
 hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

### Top CO2 Leisure sites

```{r fig.height=5}
#leisure <- fread("leisure.csv")

# Colors
custom_colors <- viridis::turbo(n = length(leisure$leisure))

# Leisure Open Street Map feature
leisure %>% 
  hchart('column', hcaes(x = leisure, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Leisure',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>% 
  hc_xAxis(title = "") %>%
  hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

### Top CO2 Natural sites

```{r fig.height=5}
#natural <- fread("natural.csv")

# Colors
custom_colors <- viridis::viridis(n = length(natural$natural))

# Natural Open Street Map feature
natural %>% 
  hchart('bar', hcaes(x = natural, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Natural',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>% 
  hc_xAxis(title = "") %>%
  hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

### Top CO2 Shop sites

```{r fig.height=5}
#shop <- fread("shop.csv")

# Colors
custom_colors <- viridis::inferno(n = length(shop$shop))

# Shop Open Street Map features
shop  %>% 
  hchart('column', hcaes(x = shop, y = ktCO2, color = custom_colors),
         options3d = list(enabled = TRUE, beta = 1, alpha = 1)) %>% 
         hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Shop',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>%
  hc_xAxis(title = "") %>%
  hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZooomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

## Row 3 {data-height="300"}

### 

```{r}

# Colors
custom_colors <- viridis::mako(n = length(OSM_road$fclass))

# Emissions by OSM road class
OSM_road %>% 
  hchart('pie', hcaes(x = fclass, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = 'Emissions by OSM road class',
           style = list(fontSize = '15px', fontWeight = 'bold')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)
  
```

### 

```{r}

# Colors
custom_colors <- viridis::cividis(n = length(place$place))

# Emissions by FRC road class
place %>% 
  hchart('pie', hcaes(x = as.factor(place), y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = 'Emissions by OSM place',
           style = list(fontSize = '15px', fontWeight = 'bold')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)
  
```

### 

```{r}

# Colors
custom_colors <- viridis::rocket(n = length(landuse$landuse))

# Emissions by landuse
landuse %>% 
  hchart('pie', hcaes(x = landuse, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = 'Emissions by OSM landuse',
           style = list(fontSize = '15px', fontWeight = 'bold')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)
```

# Street-Level Analysis {data-icon="fa-road" data-orientation="rows"}

## Emission Hotspots {data-height="600"}

## Row 1 {data-height="500" data-width="400"}

### Top 20 Emitter Streets in tCO2

```{r fig.height=5}
# Prepare street data
top_streets <- street %>%
  arrange(desc(tCO2)) %>%
  head(20) %>%
  mutate(
    name = fct_reorder(name, tCO2),
    label = paste0(name, ": ", round(tCO2, 1), " tCO₂/month"),
    color = viridis::mako(20, direction = -1)
  )
# Create treemap with improved formatting
top_streets %>%
  hchart(
    "treemap",
    hcaes(x = name, value = tCO2, color = tCO2),
    levels = list(
      list(level = 1, dataLabels = list(enabled = TRUE, 
                                      style = list(fontSize = "10px")))
    ),
    dataLabels = list(
      enabled = TRUE,
      format = "{point.name}",
      style = list(
        textOutline = "none",
        fontWeight = "normal"
      )
    )
  ) %>%
  hc_colorAxis(
    minColor = "#FCFDBF",
    maxColor = "#5B1874",
    stops = color_stops(colors = viridis::mako(5))
  ) %>%
  hc_title(text = "Street Emission Distribution") %>%
  hc_subtitle(text = "Size represents emission magnitude") %>%
  hc_credits(enabled = TRUE, text = "Zoom City Carbon Model") %>%
  hc_add_theme(hc_theme_flat()) %>%
  hc_exporting(enabled = TRUE)

```

## Street Finder {data-height="700"}

### Interactive Street Emissions Explorer

```{r}
# Prepare DT options
dt_options <- list(
  dom = 'Blfrtip',
  buttons = c('copy', 'csv', 'excel'),
  pageLength = 10,
  lengthMenu = c(5, 10, 20, 50),
  scrollX = TRUE,
  initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#2c3e50', 'color': '#fff'});",
    "}"
  ),
  columnDefs = list(
    list(targets = 0, visible = FALSE), # Hide row names
    list(targets = 1, width = '200px'), # Street name column
    list(targets = 2, width = '150px')  # Emissions column
  )
)

# Create enhanced datatable
find_street %>%
  mutate(
    ECO2_gmh = round(ECO2_gmh, 2),
    name = as.factor(name)
  ) %>%
  datatable(
    rownames = FALSE,
    colnames = c('Street Name', 'CO₂ Emissions (gram/hour)'),
    caption = htmltools::tags$caption(
      style = 'caption-side: top; text-align: left;',
      'Street-Level CO₂ Emissions Explorer'
    ),
    filter = 'top',
    extensions = c('Buttons', 'Scroller'),
    options = dt_options
  )

```

# Temporal Behaviour {data-orientation="rows" data-icon="fa-bar-chart"}

## Row {data-height="50"}

## Row {data-height="400"}

### 

```{r}
#hour <- fread("hour.csv")

# Create tibble for our line plot.  

custom_colors <- viridis::viridis(n = length(hour$date_hour))

highchart() %>% 
    hc_add_series(hour, hcaes(x = date_hour, y = ktCO2, color = custom_colors), type = "line") %>%
    hc_tooltip(crosshairs = TRUE, borderWidth = 1.5, headerFormat = "", pointFormat = paste("Hour: <b>{point.x}</b> <br> ktCO2: <b>{point.y}</b>")) %>%
    hc_title(text = "Diurnal cycle") %>% 
    hc_subtitle(text = "Traffic emissions [ktCO2/month]") %>%
    hc_xAxis(title = list(text = "Hour of day")) %>%
    hc_yAxis(title = "",
             allowDecimals = FALSE,
             plotLines = list(list(
                    color = "black", width = 1, dashStyle = "Dash", 
                    value = mean(hour$ECO2),
                    label = list(text = "Mean = 6.2", 
                                 style = list(color = "black", fontSize = 14))))) %>%
    hc_legend(enabled = FALSE) %>% 
    hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel') %>% 
    hc_add_theme(hc_theme_hcrt()) %>% 
  hc_exporting(enabled = TRUE)

```

### 

```{r}
#week <- fread("week.csv")

# Labels
wday_lables <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")

# BY weeks
week %>%
  hchart('lollipop', hcaes(x = wday_lables , y = ktCO2, color = ktCO2)) %>% 
  hc_add_theme(hc_theme_hcrt()) %>%
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_yAxis(title = list(text = '')) %>% 
  hc_xAxis(title = list(text = '')) %>% 
  hc_title(text = 'By Weekday',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel') %>% 
  hc_exporting(enabled = TRUE)

```

# About {data-icon="fa-info-circle"}

## Row {data-height="900"}

### about txt {.no-title .no-padding .colored}

<h4>**Citation**</h4>

Anjos M and Meier F (2025) Zooming into Berlin: tracking street-scale CO2 emissions based on high-resolution traffic modeling using machine learning. Front. Environ. Sci. 12:1461656. doi: [10.3389/fenvs.2024.1461656](https://doi.org/10.3389/fenvs.2024.1461656)

<h4>**Data Source**</h4>

-   Traffic counting data - <https://api.viz.berlin.de/daten/verkehrsdetektion>;
-   Open Street Map features - <https://wiki.openstreetmap.org/wiki/Map_features>;
-   Berlin Atlas data such as land use, density population, and high-level daily mean traffic volumes - <https://fbinter.stadt-berlin.de/fb/index.jsp>;
-   Meteorological data of the German Weather Service Climate Data Center - <https://opendata.dwd.de/climate_environment/CDC/>;

<h4>**People**</h4>

Developed by [Dr. Max Anjos](https://www.researchgate.net/profile/Max-Anjos/research) and Dr. Fred Meier, Chair of Climatology, TU Berlin.

<h4>**Funding**</h4>

-   CAPES -- Finance Code 001
-   Alexander Von Humboldt Foundation

<h4>**Inspiration**</h4>

Inspired by community dashboards and built using R + Flexdashboard.

<hr>

<center>

**Thanks** for visiting my first interactive FlexDashboard in R, the ZoomCityCarbonModel. Your feedback is greatly appreciated and will help me continue to improve the dashboard's functionality and design.
