---
title: "Zoom City Carbon Model"
author : "Berlin"
output: 
  flexdashboard::flex_dashboard:
    source_code: "https://github.com/ByMaxAnjos"
    vertical_layout: scroll
    social: menu
    theme: yeti
---

```{r setup, include=FALSE}
# Importing libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(flexdashboard, shiny, tidyverse, data.table, highcharter, gt, htmltools,leaflet, sf, plotly, crosstalk, viridis, DT)

library(flexdashboard)
library(shiny)
library(tidyverse)
library(data.table)
library(highcharter)
library(sf)
library(gt)
library(htmltools)
library(viridis)
library(leaflet)
library(plotly)
library(crosstalk)
library(DT)



#Load files in dashboard folder 
imap <- st_read("dashboard/data/imap.shp")
trend <- fread("dashboard/data/trend.csv")
mapCount <- fread("dashboard/data/mapCount.csv")
amenity <- fread("dashboard/data/amenity.csv")
natural <- fread("dashboard/data/natural.csv")
leisure <- fread("dashboard/data/leisure.csv")
shop <- fread("dashboard/data/shop.csv")
place <- fread("dashboard/data/place.csv")
OSM_road <- fread("dashboard/data/OSM_raod.csv")
landuse <- fread("dashboard/data/landuse.csv")
street <- fread("dashboard/data/street.csv")
hour <- fread("dashboard/data/hour.csv")
find_street <- fread("dashboard/data/find_street.csv")
week <- fread("dashboard/data/week.csv")
iDistrict_map <- st_read("dashboard/data/iDistrict.shp")
iDistrict_tibble <- fread("dashboard/data/iDistrict_table.csv") %>% 
  dplyr::select(-osm_id)

```

# Sidebar {.sidebar}

The **Zoom City Carbon Model - ZCCM** is a multi-layered, bottom-up approach for mapping and quantifying the total CO2 emissions in a city at high spatial and temporal resolutions, down to 100-meter grids or street level, and sectorial resolution. The model identifies major CO2 emitters and sinks, such as road traffic vehicles, building energy consumption, human respiration, and vegetation/soils, and estimates their emission patterns and changes over time.

This **Emission Geographic Information platform** is designed to communicate the outcomes of the {ZCCM} to users, stakeholders, the research community, and the public in general. It enables the visualization of zoom CO2 maps and summary statistics of emissions in an interactive way.

This **Flexdashboard R** leverages road traffic estimates from the ZCCM::traffic model <https://github.com/ByMaxAnjos/CO2-traffic-emissions> to showcase the spatio-temporal variability of CO2 emissions at the city level. With this tool, users can explore detailed street-level emissions, emissions associated with Open Street Map features, and temporal patterns such as hourly time series, daily cycles, and monthly totals.

**Author: Max Anjos, 2023.** [maxanjos\@campus.ul.pt](mailto:maxanjos@campus.ul.pt){.email}, Institute of Ecology Chair of Climatology, Technical University of Berlin.

# iMap {data-icon="fa-map"}

### Total Emissions {data-height="500"}

```{r fig.height=5}

# Mapping 1
#imap$col_scale <- log(1 + imap$tCO2)
pal_line <- colorFactor(palette = "Spectral", reverse = TRUE, domain = NULL)
#pal_line <- colorNumeric(reverse = TRUE, palette = "Spectral", domain = NULL)

imap$labels <- paste0(
  "<strong> name: </strong> ",
  imap$name, "<br/> ",
  "<strong> tCO2: </strong> ",
  imap$tCO2, "<br/> "
) %>%
  lapply(htmltools::HTML)

leaflet(imap) %>%
  addTiles(group = "OpenStreeMap.Default") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Esri.WorldImagery") %>%
  addProviderTiles("CartoDB.DarkMatter", group = "CartoDB.DarkMatter") %>%
  addTiles() %>%
  setView(lng = 13.406318, lat = 52.518582, zoom = 13) %>%
  addPolylines(
    #fillColor = "tCO2",
    color = ~ pal_line(tCO2),
    #fillOpacity = 0.7,
    label = ~labels,
    highlight = highlightOptions(
      color = "black",
      bringToFront = TRUE
    )
  ) %>%
  # leaflet::addLegend("bottomright",pal = pal_line, values = ~col_scale, title = "tCO2/month",
  #                    labFormat = labelFormat(prefix = "  > " , transform =  function(x) exp(x) - 1 , digits = 0)) %>% 
  leaflet::addLegend("bottomright", pal = pal_line, values = "", title = "tCO2/month") %>%
  # layers control 
  addLayersControl(
    baseGroups = c("OpenStreeMap.Default", "Esri.WorldImagery", "CartoDB.DarkMatter"),
    position = "topleft",
    options = layersControlOptions(collapsed = TRUE)
  )
```

### Trend Emissions

```{r fig.height=5}

# Create tibble for our line plot.  
#trend <- fread("trend.csv")

highchart() %>% 
    hc_add_series(trend, hcaes(x = date_day, y = ktCO2, color = ktCO2), type = "spline") %>%
    hc_tooltip(crosshairs = TRUE, borderWidth = 1.5, headerFormat = "", pointFormat =
                 paste("Day: <b>{point.x}</b> <br> ktCO2: <b>{point.y}</b>")) %>%
    hc_title(text = "") %>% 
    hc_subtitle(text = "") %>%
    hc_xAxis(title = list(text = "Day")) %>%
    hc_yAxis(title = list(text = "Traffic emissions [ktCO2/day]"),
             allowDecimals = FALSE,
             plotLines = list(list(
                    color = "white", width = 1, dashStyle = "Dash", 
                    value = mean(trend$ktCO2),
                    label = list(text = "Mean = 10", 
                                 style = list(color = "white", fontSize = 11))))) %>%
    hc_legend(enabled = FALSE) %>% 
    hc_credits(enabled = TRUE, text = '@ZoonCityCarbonModel')%>% 
    hc_add_theme(hc_theme_google()) %>% 
  hc_exporting(enabled = TRUE)

```

# Summary Stats {data-orientation="rows" data-icon="fa-bar-chart"}

## Row {data-height="100"}

## Row 1 {data-height="110"}

### Total of traffic emissions [ktCO2/month]

```{r}
#mapCount <- fread("mapCount.csv")

valueBox(round(sum(mapCount$ktCO2), digits = 2),icon = "fa-users", color = "purple")
```

### Total of carbon [ktC/month]

```{r}

valueBox(round(sum(mapCount$ktC), digits = 2), icon="fa-users", color = "purple")
```

## Row 2 {.tabset .tabset-fade}

### Top CO2 Amenity sites

```{r fig.height=5}
#amenity <- fread("amenity.csv")

# Colors
custom_colors <- viridis::plasma(n = length(amenity$amenity))

# Amenity Open Street Map feature
amenity %>% 
  hchart('bar', hcaes(x = amenity, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Amenity',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>%
 hc_xAxis(title = "") %>%
 hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

### Top CO2 Leisure sites

```{r fig.height=5}
#leisure <- fread("leisure.csv")

# Colors
custom_colors <- viridis::turbo(n = length(leisure$leisure))

# Leisure Open Street Map feature
leisure %>% 
  hchart('column', hcaes(x = leisure, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Leisure',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>% 
  hc_xAxis(title = "") %>%
  hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

### Top CO2 Natural sites

```{r fig.height=5}
#natural <- fread("natural.csv")

# Colors
custom_colors <- viridis::viridis(n = length(natural$natural))

# Natural Open Street Map feature
natural %>% 
  hchart('bar', hcaes(x = natural, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Natural',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>% 
  hc_xAxis(title = "") %>%
  hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

### Top CO2 Shop sites

```{r fig.height=5}
#shop <- fread("shop.csv")

# Colors
custom_colors <- viridis::inferno(n = length(shop$shop))

# Shop Open Street Map features
shop  %>% 
  hchart('column', hcaes(x = shop, y = ktCO2, color = custom_colors),
         options3d = list(enabled = TRUE, beta = 1, alpha = 1)) %>% 
         hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_title(text = 'Spatial association - Shop',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>%
  hc_xAxis(title = "") %>%
  hc_yAxis(title = "") %>%
  hc_credits(enabled = TRUE, text = '@ZooomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)

```

## Row 3 {data-height="300"}

### 

```{r}

# Colors
custom_colors <- viridis::mako(n = length(OSM_road$fclass))

# Emissions by OSM road class
OSM_road %>% 
  hchart('pie', hcaes(x = fclass, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = 'Emissions by OSM road class',
           style = list(fontSize = '15px', fontWeight = 'bold')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)
  
```

### 

```{r}

# Colors
custom_colors <- viridis::cividis(n = length(place$place))

# Emissions by FRC road class
place %>% 
  hchart('pie', hcaes(x = as.factor(place), y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = 'Emissions by OSM place',
           style = list(fontSize = '15px', fontWeight = 'bold')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)
  
```

### 

```{r}

# Colors
custom_colors <- viridis::rocket(n = length(landuse$landuse))

# Emissions by landuse
landuse %>% 
  hchart('pie', hcaes(x = landuse, y = ktCO2, color = custom_colors)) %>% 
  hc_add_theme(hc_theme_google()) %>% 
  hc_tooltip(pointFormat='<b>Proportion: </b> {point.percentage:,.2f}%') %>% 
  hc_title(text = 'Emissions by OSM landuse',
           style = list(fontSize = '15px', fontWeight = 'bold')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel')%>% 
  hc_exporting(enabled = TRUE)
```

# iStreets {data-orientation="rows" data-icon="fa-list"}

## Row {data-height="50"}

## Row 1 {data-height="500" data-width="400"}

### Top 20 Emitter Streets in tCO2

```{r fig.height=5}
#street <- fread("street.csv")

# Colors
custom_colors <- viridis::mako(n = length(street$name))

# Most emitter streets - treemap 
street %>% 
  head(20) %>% 
  hchart("treemap", hcaes(x = name, value = tCO2, color = tCO2), dataLabels = list(enabled = TRUE)) %>% 
  #hc_colorAxis(stops = color_stops(colors = viridis::viridis(20))) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel') %>% 
  hc_exporting(enabled = TRUE) 

```

## Row 2 {data-height="900" data-width="800"}

### Find your street

```{r}
#find_street <- fread("find_street.csv")
find_street %>% 
  datatable(
caption="Top 20 emitter streets",
rownames=T,
filter="top",
options = list(pageLength = 20
))

```

# Temporal Behaviour {data-orientation="rows" data-icon="fa-bar-chart"}

## Row {data-height="50"}

## Row {data-height="400"}

### 

```{r}
#hour <- fread("hour.csv")

# Create tibble for our line plot.  

custom_colors <- viridis::viridis(n = length(hour$date_hour))

highchart() %>% 
    hc_add_series(hour, hcaes(x = date_hour, y = ktCO2, color = custom_colors), type = "line") %>%
    hc_tooltip(crosshairs = TRUE, borderWidth = 1.5, headerFormat = "", pointFormat = paste("Hour: <b>{point.x}</b> <br> ktCO2: <b>{point.y}</b>")) %>%
    hc_title(text = "Diurnal cycle") %>% 
    hc_subtitle(text = "Traffic emissions [ktCO2/month]") %>%
    hc_xAxis(title = list(text = "Hour of day")) %>%
    hc_yAxis(title = "",
             allowDecimals = FALSE,
             plotLines = list(list(
                    color = "black", width = 1, dashStyle = "Dash", 
                    value = mean(hour$ECO2),
                    label = list(text = "Mean = 6.2", 
                                 style = list(color = "black", fontSize = 14))))) %>%
    hc_legend(enabled = FALSE) %>% 
    hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel') %>% 
    hc_add_theme(hc_theme_hcrt()) %>% 
  hc_exporting(enabled = TRUE)

```

### 

```{r}
#week <- fread("week.csv")

# Labels
wday_lables <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")

# BY weeks
week %>%
  hchart('lollipop', hcaes(x = wday_lables , y = ktCO2, color = ktCO2)) %>% 
  hc_add_theme(hc_theme_hcrt()) %>%
  hc_tooltip(pointFormat = '<b>ktCO2: </b> {point.y} <br>') %>% 
  hc_yAxis(title = list(text = '')) %>% 
  hc_xAxis(title = list(text = '')) %>% 
  hc_title(text = 'By Weekday',
           style = list(fontSize = '25px', fontWeight = 'bold')) %>% 
  hc_subtitle(text = 'Traffic emissions [ktCO2/month]',
              style = list(fontSize = '16px')) %>% 
  hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel') %>% 
  hc_exporting(enabled = TRUE)

```

# iDistrict {data-icon="fa-search"}

## Column {data-width="400"}

### Find your disctrict

**Get here:**

```{r}

# Create shared data that will be used to link filters, data table, and line plot. 
  iDistrict_tibble$day <- as.numeric(iDistrict_tibble$day)
  shared_data <- SharedData$new(iDistrict_tibble, group = 'hello')
  
  # Create filter for year and district These filters will adjust the DT datatable and PLOTLY plot. 
  filter_slider("day", "Day", shared_data, ~day, step = 1)
  filter_select("district", "District", shared_data, ~district, allLevels = TRUE, multiple = TRUE)
  filter_checkbox(id = "district", label = "Select district", sharedData = shared_data, group = ~district,
                  columns=2)
  

# # Create datatable. 
# datatable(shared_data,
#           rownames = FALSE,
#           colnames = c('tCO2', 'Day', 'District'),
#           class = 'cell-border stripe',
#           width = '100%',
#           extensions = "Scroller",
#           options=list(deferRender = FALSE, 
#                        scrollY = 280, 
#                        scrollCollapse = TRUE,
#                        scroller = TRUE,
#                        dom = 't'))

# # iDistrict
# df_sum <- iDistrict_map %>%
#   group_by(district) %>%
#   summarize(ktCO2 = round(sum(tCO2)/1000, digits = 2)) %>% 
#   na.omit()
# 
# highchart() %>%
#   hc_chart(polar = TRUE, type = "column") %>%
#   hc_title(text = "Traffic emissions by district in ktCO2", 
#            style = list(fontSize = '25px', fontWeight = 'bold')) %>%
#   hc_xAxis(categories = df_sum$district, tickmarkPlacement = "on", lineWidth = 0) %>%
#   hc_yAxis(gridLineInterpolation = "polygon", lineWidth = 0, min = 0,  title = list(text = "")) %>%
#   hc_add_series(data = df_sum$ktCO2, name = "ktCO2/month") %>% 
#   hc_credits(enabled = TRUE, text = '@ZoomCityCarbonModel') %>% 
#     hc_add_theme(hc_theme_ffx())%>% 
#   hc_exporting(enabled = TRUE)

```

### 

```{r}

# Set a random seed. We will do this so that we can reproduce the random sample of colors we will use for our next graph. 
set.seed(80085)

# Create line graph. 
plot_ly(shared_data, x = ~day, y = ~tCO2, 
       color = ~district, colors = sample(colours(), 120),
       type = 'scatter', mode = 'lines',
       hoverinfo = 'text', text = ~paste("District: ", 
                                         district, '<br>Day: ', day, "<br>tCO2: ", tCO2)) %>%
       layout(showlegend = FALSE,
              title = "trafiic emissions by Disrrict",
              xaxis = list(title = "Day"),
              yaxis = list(title = " tCO2")) %>%
       layout(plot_bgcolor = 'transparent') %>% 
       layout(paper_bgcolor = 'transparent') %>% 
       add_markers() %>% 
       highlight("plotly_click")
  
```

## Column {data-width="600"}

### Interactive map

```{r map}

pal_line <- colorFactor(palette = "viridis", domain = NULL, reverse = TRUE)
iDistrict_map$labels <- paste0(
  "<strong> district: </strong> ",
  iDistrict_map$district, "<br/> ",
  "<strong> tCO2: </strong> ",
  iDistrict_map$tCO2, "<br/> "
) %>%
  lapply(htmltools::HTML)

leaflet(iDistrict_map) %>%
  addTiles(group = "OpenStreeMap.Default") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Esri.WorldImagery") %>%
  addProviderTiles("CartoDB.DarkMatter", group = "CartoDB.DarkMatter") %>%
  addPolygons(weight = 1, smoothFactor = 0.5,
    #fillColor = "tCO2",
    color = ~ pal_line(tCO2),
    opacity = 1.0, fillOpacity = 0.5,
    label = ~labels,
    highlight =  highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE)
  ) %>%
  leaflet::addLegend(pal = pal_line, values = "",title = "Traffic tCO2 emissions", group = "Total of tCO2") %>% 
  # layers control
  addLayersControl(
    baseGroups = c("OpenStreeMap.Default", "CartoDB.DarkMatter", "Esri.WorldImagery"),
    position = "topleft",
    options = layersControlOptions(collapsed = TRUE)
  )

```

### 

```{r}
set.seed(80085)
plot_ly(shared_data, y = ~tCO2, x = ~district, type = 'bar', color = ~district, colors = sample(colours(), 120)) %>%
       layout(yaxis = list(categoryorder = "trace"))

```

# About {data-icon="fa-info-circle"}

Row {data-height=900}
-----------------------------------------------------------

### about txt {.no-title .no-padding .colored}

<h4>**Related Works**</h4>

* Anjos, M.; Meier, F. Zooming into City and tracking CO2 traffic emissions at street level. Carbon Balance and Management(submitted).
* Anjos, M.; Meier, F. City Carbon Budget and hourly net CO2 fluxes at 0.01º resolution for informed climate action (in preparation).

<h4>**Data Source**</h4>

* Traffic counting data -  https://api.viz.berlin.de/daten/verkehrsdetektion; 
* Open Street Map features - https://wiki.openstreetmap.org/wiki/Map_features; 
* Berlin Atlas data such as land use, density population, and high-level daily mean traffic volumes - https://fbinter.stadt-berlin.de/fb/index.jsp;
* Meteorological data of the German Weather Service Climate Data Center - https://opendata.dwd.de/climate_environment/CDC/; 

<h4>**People**</h4>

The development of this interative platform was led by [Dr. Max Anjos](https://www.researchgate.net/profile/Max-Anjos/research) and joined by Dr.Fred Meier, and it is hosted at the [Chair of Climatology, Institute of Ecology, Technische Universität Berlin](https://www.klima.tu-berlin.de/index.php?show=home_start&lan=en).

<h4>**Funding**</h4>

This project is was financed in part by the Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) – Finance Code 001, and by the Alexander Von Humboldt Foundation.

<h4>**Inspiration**</h4>

After being inspired by Tavoosi's amazing interactive dashboard on suicide data (available at https://www.kaggle.com/tavoosi/suicide-data-full-interactive-dashboard) and by DSangeetha's nice dashboard on Zomato Restaurants Data (https://www.kaggle.com/code/devisangeetha/interactive-flexdashboard-in-r/report), this dashboard was created.

<hr>

<center>
**Thanks** for visiting my first interactive FlexDashboard in R, the ZoomCityCarbonModel. 
Your feedback is greatly appreciated and will help me continue to improve the dashboard's functionality and design.




